Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-03 paper.tex
reviewed section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Automated and formal verification have been employed to ensure the correctness and reliability of ECPS during the last decade, as well as controller synthesis for ECPS and HS \textcolor{red}{add citations}. A ECPS $S$ is a tuple $S=(X,X_{0},U,Y,r,v)$, where $X$ is a set of reachable states, $X_{0}$ is a set of initial states, $U$ is a set of inputs, $Y$ is the set of outputs, $r$ is a transition function such that $r:X\times U \rightarrow X$, and  $v$ is an output mapping function such that $v:X\times U \rightarrow Y$~\cite{Rungger16,Alur00,Girard11}.

The overall formal and automated synthesis process for ECPS and HS involves three main steps: \textit{modeling}, which is related to obtain a sound mathematical representation able to capture all relevant aspects of continuous and discrete dynamics and their interaction, as well as, formulate properties and invariants that describe the desirable behavior; \textit{verification}, where the ECPS behavior is checked through the proposed mathematical structure and the attendance of the desired behavior is verified; and, finally, the controller \textit{synthesis} itself, that produces a controller or finds invariant control laws that allow the ECPS, modeled according to the first step (\textit{modeling}), to meet the requirements and behave as desired, as confirmed by the verification step.

@@

Rungger and Tabuada~\cite{Rungger16} and Tabuada et al.~\cite{Tabuada14} proposed a general and wide model for ECPS based on hybrid automata, providing the concept of robustness and important tools for robust stability analysis for ECPS.

@@

Given a class of ECPS's $\Omega$ and a set $\Phi$ of desired properties, a class of verification problems is called decidable, if there is an algorithm that is able to decide in a finite number of steps whether $\forall \mathcal{O}\in\Omega$ satisfies every property $\mathcal{L}\in \Phi$~\cite{Alur00}. Decidability is a key issue in ECPS verification, since there are uncountable states and complex dynamics to be considered, {\it i.e.}, hybrid automata and their variations (usually employed to model ECPS) are infinite-state machines~\cite{Henzinger95}. Generally, the properties that must be hold for ECPS are related to safety, liveness, and reachability. In particular, model checking procedures have been employed to verify these properties of model programs even under undecidability conditions via approximations, {\it e.g.}, bounding the number of steps from the initial state, which leads to bounded model checking~\cite{Veanes09}.

>>>>

Automated formal verification have been employed to ensure the correctness and reliability of ECPS during the last decade, as well as controller synthesis for ECPS and HS \textcolor{red}{add citations}.

A ECPS $S$ can be represented as a tuple $S=(X,X_{0},U,Y,r,v)$, where $X$ is a set of reachable states, $X_{0}$ is a set of initial states, $U$ is a set of inputs, $Y$ is the set of outputs, $r$ is a transition function such that $r:X\times U \rightarrow X$, and  $v$ is an output mapping function such that $v:X\times U \rightarrow Y$~\cite{Rungger16,Alur00,Girard11}.

The overall automated formal synthesis process for ECPS and HS involves three main steps: \textit{modeling}, which is related to obtain a sound mathematical representation able to capture all relevant aspects of continuous and discrete dynamics and their interaction, as well as, formulate properties and invariants that describe the desirable behavior; \textit{verification}, where the ECPS behavior is checked through the proposed mathematical structure and the attendance of the desired behavior is verified; and, finally, the controller \textit{synthesis} itself, that produces a controller or finds invariant control laws that allow the ECPS to meet the requirements and behave as desired, which is confirmed by a verification oracle.

@@

Rungger and Tabuada~\cite{Rungger16} and Tabuada {\it et al.}~\cite{Tabuada14} proposed a general and wide model for ECPS based on hybrid automata, providing the concept of robustness and important tools for robust stability analysis for ECPS.

@@

Given a class of ECPS's $\Omega$ and a set $\Phi$ of desired properties, a class of verification problems is called decidable, if there is an algorithm that is able to decide in a finite number of steps whether $\forall \mathcal{O}\in\Omega$ satisfies every property $\mathcal{L}\in \Phi$~\cite{Alur00}. Decidability is a key issue in ECPS verification, since there are uncountable states and complex dynamics to be considered, {\it i.e.}, hybrid automata and their variations (usually employed to model ECPS) are infinite-state machines~\cite{Henzinger95}. Generally, the properties that must hold for ECPS are related to safety, liveness, and reachability. In particular, model checking procedures have been employed to verify these properties of model programs even under undecidability conditions via approximations, {\it e.g.}, bounding the number of steps from the initial state, which leads to bounded model checking~\cite{Veanes09}.
